Figures

### 2019-05-30 figures/07_model-selection.Rmd
add resid dotplot to makefile

```{r 07_model_selection, fig.height=3, echo=FALSE}

@@

```{r residual_dotplot, echo=FALSE}
fit <- readRDS("data/mcmc/re/tn_corn")

get_residuals <- function(model, threshold = 0.1){
  # model <- re_brms[[1]]
  model$res_med <- dt %>%
    add_residual_draws(model) %>%
    group_by(lagoslakeid) %>%
    summarize(.residual_median = median(.residual)) %>%
    left_join(dplyr::select(lg$locus, lagoslakeid, nhd_lat, nhd_long),
              by = "lagoslakeid")

@@

states_lg <- 
  state_sf()[unlist(lapply(st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)), function(x) length(x) > 0)),]

>>>>

```{r 07_model_selection, fig.height=3, echo=FALSE,eval=FALSE}

@@

```{r residual_dotplot, echo=FALSE}
library(tidybayes)
library(brms)

fit <- readRDS("../data/mcmc/re/tn_corn")

dt        <- readRDS("../data/dt_scaled.rds") 
names(dt) <- gsub("_", "v", names(dt))

good_hu4s <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally() %>%
  dplyr::filter(n >= 3)
dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)

get_residuals <- function(model, threshold = 0.1){
  # model <- fit
  model$res_med <- dt %>%
    add_residual_draws(model) %>%
    group_by(lagoslakeid) %>%
    summarize(.residual_median = median(.residual)) %>%
    left_join(dplyr::select(lg$locus, lagoslakeid, nhd_lat, nhd_long),
              by = "lagoslakeid")

@@

states_lg <- state_sf()[
  unlist(lapply(
    st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)),
    function(x) length(x) > 0)),]
